Practical Optional Types for Clojure

### 2015-02-19 intro.tex
use minted for syntax highlighting

\begin{lstlisting}
(ann parent [(U nil File) -> (U nil File)])
(defn parent [^File f]
  (when f
    (let [s (. f (getParent))]
      (assert s "Expected parent string, got nil")
      (new File s))))
\end{lstlisting}

@@

\begin{lstlisting}
(defalias Expr
  (U '{:op :if :test Expr :then Expr :else Expr}
     '{:op :const :val Any} ...))
(ann tree-str [Expr -> String])
(defmulti tree-str (fn [e :- Expr] (get :op e)))
(defmethod tree-str :if [{:keys [test then else]}] 
  (str (tree-str test) (tree-str then) (tree-str else)))
(defmethod tree-str :const [{:keys [val]}] 
  (str val))
\end{lstlisting}

>>>>

\begin{minted}[]{clojure}
(ann parent [(U nil File) -> (U nil File)])
(defn parent [^File f]
  (when f
    (let [s (. f (getParent))]
      (assert s "Expected parent string, got nil")
      (new File s))))
\end{minted}

@@

\begin{minted}[mathescape,
  frame=lines,
  framesep=2mm]{clojure}
(defalias Expr
  (U '{:op :if :test Expr :then Expr :else Expr}
     '{:op :const :val Any} ...))
(ann tree-str [Expr -> String])
(defmulti tree-str (fn [e :- Expr] (get :op e)))
(defmethod tree-str :if [{:keys [test then else]}] 
  (str (tree-str test) (tree-str then) (tree-str else)))
(defmethod tree-str :const [{:keys [val]}] 
  (str val))
\end{minted}
